---
title: "My silly report"
author: "Zach Shunnarah"
date: "6/24/2021"
output: html_document
bibliography: bibliography.bib
---

```{r, include=FALSE, echo = TRUE, eval = TRUE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = TRUE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE)
```


```{r,echo = FALSE}
library(dplyr)
smoke <- c(TRUE, TRUE, TRUE, TRUE, TRUE,
           TRUE, FALSE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, 
           FALSE, FALSE, FALSE, TRUE, TRUE)
age <- c(35, 21, 20, 48, 20, 20, 22, 19, 19, 20, 19, 18, 
         24, 22, 22, 19, 21, 19, 21)
people <- data.frame(smoke, age)
people <- people %>%
  filter(age <= 34)

obs <- nrow(people)
```

# Introduction

## Background

### Smoking: is it good for you?

Everyone knows that smoking is bad for you. And everyone knows that math is pretty easy [@Rudd2014]. Doctors probably should not drink on call [@Peterman2005].

### How many people smoke?

Lots of people smoke.

# **Methods**

My esteemed colleagues and I surveyed `r obs` people. The average age of the participants was `r round(mean(people$age))` years. That is very _young_. **Right?**


# **Results**

The below chart shows the age of participants.

```{r, echo = FALSE}
library(ggplot2)

ggplot(people,
       aes(age,
           smoke),
       fill = ) +
  geom_boxplot()

```

# Conclusion

Some people have smoked. Others have not.

# Bibliography